\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{caption}

\geometry{margin=1in}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\begin{document}

\begin{titlepage}
    \centering
    \vspace*{1cm}
    \Huge \textbf{Web Technology Lab 06} \\
    \Large \textbf{Node.js App (Backend) + GitHub Skeleton Setup} \\
    \vspace{1.5cm}
    \textbf{Submitted By:} \\
    Kunal Sharma \\
    CS-2341057 \\
    3CSE15 (G1) \\
    \vspace{0.8cm}
    \textbf{Instructor:} \\
    Mr. Dibyanarayan Hazra \\
    \vfill
    IILM University, Greater Noida \\
    \today
\end{titlepage}

\tableofcontents
\newpage

\section{Introduction}
This lab focuses on establishing a full-stack project architecture. We create a dual-folder repository structure containing a Node.js Express backend and a placeholder for a Vite-based React frontend. The primary objective is to demonstrate environment configuration, route handling, and version control best practices by pushing the skeleton to GitHub.

\section{Essential Commands Followed}
The following commands were used to initialize the project environment:

\begin{lstlisting}[language=bash]
mkdir lab06-node-fullstack-skeleton && cd lab06-node-fullstack-skeleton
mkdir backend frontend
git init
# Inside backend/
npm init -y
npm i express cors dotenv
npm i -D nodemon
# Inside frontend/ (Placeholder initialization)
npm create vite@latest . -- --template react
\end{lstlisting}

\section{Project Structure}
The repository follows a strict hierarchy as required by the handout:
\begin{itemize}
    \item \textbf{backend/}: Contains the server logic.
    \item \textbf{frontend/}: Vite placeholder for future UI components.
    \item \textbf{.gitignore}: Configured to exclude \texttt{node\_modules} and \texttt{.env} files.
    \item \textbf{.env}: Centralized environment variables for the root level.
\end{itemize}

\section{Backend Implementation}
The backend uses Express for routing. A centralized \texttt{.env} file is used to manage the \texttt{PORT} and \texttt{DB\_LINK}.

\subsection{Centralized .env File}
\begin{lstlisting}[caption=Root .env file]
PORT=3000
DB_LINK=mongodb+srv://kunal:sushi_rocks_2026@cluster0.mongodb.net/...
\end{lstlisting}

\subsection{Server Configuration}
\begin{lstlisting}[language=JavaScript, caption=backend/src/server.js]
const express = require("express");
const cors = require("cors");
const dotenv = require("dotenv");

dotenv.config({ path: '../.env' }); 

const app = express();
app.use(cors());

const PORT = process.env.PORT || 3000;

app.get("/", (req, res) => res.send("Lab 06: Backend running and GitHub push successful"));
app.get("/about", (req, res) => {
    res.send("Name: Kunal Sharma | Enrollment: CS-2341057 | Section: 3CSE15 (G1)");
});
app.get("/health", (req, res) => res.json({ status: "ok" }));

app.listen(PORT, () => console.log(`Server running at http://localhost:${PORT}`));
\end{lstlisting}

\section{GitHub Push History}
The code was pushed to the GitHub repository using the following sequence:
\begin{enumerate}
    \item \texttt{git add .}
    \item \texttt{git commit -m "Lab 06: add backend + frontend skeleton"}
    \item \texttt{git branch -M main}
    \item \texttt{git remote add origin <URL>}
    \item \texttt{git push -u origin main}
\end{enumerate}

\section{Conclusion}
The Lab 06 project skeleton is successfully established. The backend provides student information via RESTful routes and correctly retrieves configuration from a centralized environment file.

\end{document}
